Topological approach to finding blackholes in directed networks

### 2019-12-06 blackholes/pavt/article.tex
Section 1.1 is done

@@

We will need the following statement to discuss issues of known approaches.
\begin{lemma}
Given graph $G(V,E)$, blackhole $B \subseteq V$, SCC $S \subseteq V$ and $v \in V : v \in S$. Then $\forall s \in S$ will be true $s \in B$.
If any node in SCC belongs to blackhole, then all the nodes of this SCC belong to the same blackhole.
\end{lemma}
\begin{proof}
    In SCC any node is reachable from any other node. This means, that any node in SCC contains the whole SCC in its closure.
\end{proof}

@@

% Previously 
Authors from the University of New Jersey gave \cite{li2010detecting} general and simplified problem formulation for blackhole search
in directed graph.

The main contributor to the topic is the New Jersey University. They both formulated the task and provided an algorithm for
blackhole detection in case of unweighted directed graph \cite{li2010detecting}. Two years later they published an algorithm
for approximate blackholes search in general case (weighted graph)\cite{li2012mining,li2014mining}. Hong et al \cite{hong2015detecting} had
an unusual application for blackhole mining in the city environment. They introduced original algorithm. Semenov et al. \cite{semenov2017survey}
in 2017 provided a survey of common approaches to anti - money laundering by graph mining.

>>>>

Semenov et al. \cite{semenov2017survey}
in 2017 provided a survey of common approaches to anti - money laundering by graph mining.

The online detection of black holes/volcanos can timely
reflect anomalous events, such as disasters, catastrophic accidents,
and therefore help keep public safety \cite{hong2015detecting}.

@@

We will need the following statement to discuss issues of known approaches.
\begin{lemma}
For a given graph $G(V,E)$, SCC $S \subseteq V,\ blackhole\ B \subseteq V$ if $\ \exists v \in S: v \in B$,  then $\forall s \in S$ will be true $s \in B$.
In other words, if any node in SCC belongs to a blackhole, then all the nodes of this SCC belong to the same blackhole.
\end{lemma}
\begin{proof}
    In SCC any node is reachable from any other node. This means, that any node $v$ in SCC contains the whole SCC in its closure. By Lemma 3 the whole SCC belongs to the same blackhole as $v$. 
\end{proof}

@@

% Previously 
%Authors from the University of New Jersey gave \cite{li2010detecting} general and simplified problem formulation for blackhole search
in directed graph.

The main contributor to the blackhole detecting problem is the authors from the University of New Jersey. They both formulated the task and provided an algorithm for blackhole detection in case of unweighted directed graph \cite{li2010detecting}. 
Two years later they published an algorithm for approximate blackhole search in general case (weighted graph) \cite{li2012mining,li2014mining}. 
Hong et al \cite{hong2015detecting} had
an unusual application for blackhole mining in the city environment. They introduced an original algorithm.
